From Object Classification to Naming: Modeling Entry-level Names for Real-world Objects

### 2019-12-10 papers/ACL2020/analysis.tex
[ACL2020] ...

\paragraph{Error Categories} We categorize model predictions into the following types (see also Figure~\ref{fig:mistakes} for examples):\\
Besides \textit{Hit}, the entry-level name, and \textit{Off}, a non-sensical name (none of the others), we distinguish between different \textit{Human-like mishits}:
\begin{tabularx}{.49\textwidth}{lX}
	\sameobject: & an alternative name for the object (see Section~\ref{sect:mn_verification}), or a synonym or a hypernym (\name{house/building}) \\
	OtherObject & a name produced by annotators, but not an alternative of the entry-level name \\
	LowCount: & a name produced by one annotator\\
	Related:& a hyponym or co-hyponym of the entry-level (\textit{jacket/shirt})
\end{tabularx}
\iffalse
\begin{itemize}
	\item \sameobject: an alternative name for the object (see Section~\ref{sect:mn_verification}), or a synonym or a hypernym (\name{house/building})
	\item OtherObject: a name produced by annotators, but not an alternative of the entry-level name 
	\item LowCount: a name produced by only one annotator
	\item Related: a hyponym or co-hyponym of the entry-level (\textit{jacket/shirt})
\end{itemize}
\fi

>>>>

\paragraph{Error Categories} We categorize model predictions into the following types (see also Figure~\ref{fig:mistakes} for examples): 
Besides \textit{Hit}, the entry-level name, and \textit{Off}, a non-sensical name (none of the others), we distinguish between different \textit{Human-like mishits}:\\\vspace{-2ex}

\begin{tabularx}{.46\textwidth}{@{~}lX}
	\sameobject: & an alternative name for the object (see Section~\ref{sect:mn_verification}), or a synonym or a hypernym (\name{house/building}) \\
	OtherObject & a name produced by annotators, but not an alternative of the entry-level name \\
	LowCount: & a name produced by one annotator\\
	Related:& a hyponym or co-hyponym of the entry-level (\textit{jacket/shirt})\\
\end{tabularx}
\iffalse
\begin{itemize}
	\item \sameobject: an alternative name for the object (see Section~\ref{sect:mn_verification}), or a synonym or a hypernym (\name{house/building})
	\item OtherObject: a name produced by annotators, but not an alternative of the entry-level name 
	\item LowCount: a name produced by only one annotator
	\item Related: a hyponym or co-hyponym of the entry-level (\textit{jacket/shirt})
\end{itemize}
\fi
